---
title: "Quiz2"
output: pdf_document
---

Q1. Suppose I define the following function in R
```{r eval=FALSE}
cube <- function(x, n) {
        x^3
}
```
What is the result of running
```{r eval=FALSE}
cube(3)
```
in R after defining this function?

```{r}
cube <- function(x, n) {
  x^3
}
cube(3)
```

Q2. The following code will produce a warning in R.
```{r eval=FALSE}
x <- 1:10
if(x > 5) {
        x <- 0
}
```
Why?

```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
```

Q3. Consider the following function
```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
```
If I then run in R
```{r eval=FALSE}
z <- 10
f(3)
```
What value is returned?

```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
z <- 10
f(3)
```

Q4. Consider the following expression:
```{r eval=FALSE}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```
What is the value of 'y' after evaluating this expression?

```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
y
```

Q5. Consider the following R function
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
Which symbol in the above function is a free variable?

```{r eval=FALSE}
f
```