---
title: "Quiz1"
output: html_document
---

Q4. If I execute the expression x <- 4 in R, what is the class of the object 'x' as determined by the 'class()' function?
```{r}
x <- 4
class(x)
```

Q5. What is the class of the object defined by the expression x <- c(4, "a", TRUE)?
```{r}
x <- c(4, "a", TRUE)
class(x)
```

Q6. If I have two vectors x <- c(1,3, 5) and y <- c(3, 2, 10), what is produced by the expression cbind(x, y)?
```{r}
x <- c(1,3, 5)
y <- c(3, 2, 10)
cbind(x,y)
```

Q8. Suppose I have a list defined as x <- list(2, "a", "b", TRUE). What does x[[1]] give me?
```{r}
x <- list(2, "a", "b", TRUE)
x[[1]]
```

Q9. Suppose I have a vector x <- 1:4 and a vector y <- 2. What is produced by the expression x + y?
```{r}
x <- 1:4
y <- 2
x+y
```

Q10. Suppose I have a vector x <- c(3, 5, 1, 10, 12, 6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this?
```{r}
x <- c(3, 5, 1, 10, 12, 6)
x[x <= 5] <- 0
x
```

```{r warning = FALSE, message = FALSE}
# loading data to Q11-Q20
library(RCurl)
z <- getURL("https://raw.githubusercontent.com/offff/Coursera---R-Programming/master/hw1_data.csv")
Q1_dataset <- read.csv(text = z)
```

Q11. In the dataset provided for this Quiz, what are the column names of the dataset?
```{r}
colnames(Q1_dataset)
```

Q12. Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
Q1_dataset[1:2,]
```

Q13. How many observations (i.e. rows) are in this data frame?
```{r}
dim(Q1_dataset)[1]
```

Q14. Extract the last 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
n <- dim(Q1_dataset)[1]
m <- n-1
Q1_dataset[m:n,]
```

Q15. What is the value of Ozone in the 47th row?
```{r}
Q1_dataset[47,1]
```

Q16. How many missing values are in the Ozone column of this data frame?
```{r}
sum(is.na(Q1_dataset$Ozone))
```

Q17. What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
```{r}
mean(Q1_dataset$Ozone, na.rm = T)
```

Q18. Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
subset1 <- Q1_dataset[Q1_dataset$Ozone > 31,]
subset2 <- subset1[subset1$Temp > 90,]
subset3 <- na.omit(subset2)
mean(subset3$Solar.R)
```

Q19. What is the mean of "Temp" when "Month" is equal to 6?
```{r}
subset4 <- Q1_dataset[Q1_dataset$Month == 6,]
subset5 <- na.omit(subset4)
mean(subset4$Temp)
```

Q20. What was the maximum ozone value in the month of May (i.e. Month = 5)?
```{r}
subset6 <- Q1_dataset[Q1_dataset$Month == 5,]
max(na.omit(subset6$Ozone))
```

